Visualization of [fulle name] Fractional Integrals

### 2019-04-11 fractional/CMJ style files/article-template.tex
added more text to example section

We can assign a geometric interpretation to the above fractional integrals by converting them into Cavalieri integrals. This can be achieved by first 
converting the above integrals into Riemann-Stieltjes integrals and then converting the resulting integrals into Cavalieri integrals. We can convert fractional 
integral into Riemann-Stieltjes integrals by utilizing Eq.~\eqref{}. Riemann
The inegrator $g_t^{\alpha}(\tau)$ of the aforementioned intermediate Riemann-Stieltjes integrals are equal and independent of the integrand $f(\tau)$.
The set of functions $\{g_{10}^{\alpha}(\tau)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$ are presented in Table \textbf{??}.

>>>>

We can assign a geometric interpretation to the above fractional integrals by converting them into Cavalieri integrals. This can be achieved by first 
converting the above integrals into Riemann-Stieltjes integrals and then converting the resulting integrals into Cavalieri integrals. Exaclty how these conversion are 
to be performed is discussed in the previous section. The inegrator $g_t^{\alpha}(\tau)$ of the aforementioned intermediate Riemann-Stieltjes integrals are equal and independent of the integrand $f(\tau)$.
The set of functions $\{g_{10}^{\alpha}(\tau)|\alpha\in\{0,0.2,\cdots,0.8,1\}\}$ are presented in Table \textbf{??}. The integration limits of the aformentioned Cavalieri 
integrals are functions and are determined by the integrand $f(\tau)$ and the integrator $g_t^{\alpha}(\tau)$. The shape of the infini
